---
title: "STA304 A2Group 21"
author: "Yingshi Wang"
date: "10/6/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("tidyverse")
library(tidyverse)
library(ggplot2)
```

1. A political party: Liberal Party
2. A geographic focus: Ontario
3. Survey methodology:
  • What is the population, frame, and sample?
  Population: a Canadian citizen aged 18 or older on election day and provide acceptable proof of identity and address.
  Frame: Gender
  • What sampling methods will you use and why? What are some of the statistical properties that the method brings to the table?
  Stratified Sampling
  • How are you going to reach your desired respondents?
  Online survey
  • How much do you estimate this will cost?
  Survey Monkey cost
  • What steps will you take to deal with non-response and how will non-response affect your survey?
  According to percentage of non-response, we have different data imputation
  • How are you going to protect respondent privacy?

```{r}
set.seed(123456)
#Are you eligible and registered to vote at your current address you living at?(Yes=1/No=1)
if.eligible <- rbernoulli(1000, p = 0.9) 
if.eligible <- ifelse(if.eligible == TRUE, 'Yes','No')
```

```{r}
#Q2 What is the highest level of education you have completed?
#https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/hlt-fst/edu-sco/Table.cfm?Lang=E&T=11&Geo=00&SP=1&view=2&age=2&sex=1
edu <- c("No certificate","less than high school degree", "high school degree or equivalent", "non-university certificate or diploma below bachelor level", "bachelor degree or highter")
data <- data.frame(if.eligible)
data$edu <- NA
num.yes <- nrow(data[data$if.eligible == 'Yes',])
num.no <- nrow(data[data$if.eligible == 'No',])

edu.yes <- sample(edu, num.yes, replace = TRUE, prob = c(0,0.104, 0.245, 0.306, 0.345))
edu.no <- sample(edu, num.no, replace = TRUE, prob = c(0.19,0.81, 0, 0, 0))
data[data$if.eligible == 'Yes', "edu"] <- edu.yes
data[data$if.eligible == 'No', "edu"] <- edu.no
```

```{r}
# Q3 Do you think marijuana legalization should be allowed?  Completely agree=1, somewhat agree=2,neutrally=3,somewhat disagree=4, completely disagree=5
# https://abacusdata.ca/canadians-are-ready-for-legal-cannabis/
marijuana <- c("Completely agree","somewhat agree", "high school degree or equivalent", "neutrally", "somewhat disagree","completely disagree")
marijuana<-sample(marijuana,size=1000,prob=c(0.25,0.21,0.24,0.12,0.18),replace=TRUE)
```

```{r}
#Q4 In general, what do you think about loosened the rules for refugee?(1-5)
#https://www.cicnews.com/2019/04/majority-of-canadians-maintain-positive-views-of-immigration-new-survey-finds-0412240.html#gs.i5mh19
refugee <- c("Completely agree","somewhat agree", "high school degree or equivalent", "neutrally", "somewhat disagree","completely disagree")
refugee<-sample(refugee,size=1000,replace=TRUE,prob=c(0.2,0.25,0.35,0.12,0.08))
```

```{r}
#Q5 Do you think everyone should be permitted to possess guns? Yes=1,No=0
set.seed(5)
data1 <- data.frame(Sex)
data1$Gun <- NA
n.male <- nrow(data1[data1$Sex == 'Male',])
n.female <- nrow(data1[data1$Sex == 'Female',])

Gun <- c("Yes", "No")
Gun_data_male <- sample(Gun, n.male, replace = TRUE, prob = c(0.1, 0.9))
Gun_data_female <- sample(Gun, n.female, replace = TRUE, prob = c(0.05, 0.95))
data1[data1$Sex == 'Male', "Gun"] <- Gun_data_male
data1[data1$Sex == 'Female', "Gun"] <- Gun_data_female

ggplot(data1, aes(x = Sex, fill = Gun)) + geom_bar()
```

```{r}
#Q6 Do you agree with environmental safety is one of the priorities to Canada? 1-5
Q6<-sample(1:5,size=1000,replace=TRUE)
```


```{r}
# Which party are you going to vote on Election Day? 1- Liberal 2-Political 3-Quec 4-Green 5-Conservative
Q7 <- sample(1:5,size=1000,replace=TRUE)
```

```{r}
data$marijuana <- marijuana
data$refugee <- refugee
ggplot(data, aes(x = if.eligible,fill=edu)) + geom_bar()
ggplot(data, aes(marijuana)) +
  geom_bar(fill = "#4073D1AF") + ggtitle("Social acceptability on Cannabis legalization") 
ggplot(data, aes(refugee)) +
  geom_bar(fill = "#8473A4AB") + ggtitle("Canadian social acceptability on accepting more refugees")  
```

