---
title: "STA304 A2Group 21"
author: "Yingshi Wang"
date: "10/6/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. A political party: Liberal Party
2. A geographic focus: Ontario
3. Survey methodology:
  • What is the population, frame, and sample?
  Population: a Canadian citizen aged 18 or older on election day and provide acceptable proof of identity and address.
  Frame: Gender
  • What sampling methods will you use and why? What are some of the statistical properties that the method brings to the table?
  Stratified Sampling
  • How are you going to reach your desired respondents?
  Online survey
  • How much do you estimate this will cost?
  Survey Monkey cost
  • What steps will you take to deal with non-response and how will non-response affect your survey?
  According to percentage of non-response, we have different data imputation
  • How are you going to protect respondent privacy?

```{r}
set.seed(123456)
#Are you eligible and registered to vote at your current address you living at?(Yes=1/No=1)
Q1<-sample(0:1,size=500,replace=TRUE)
# What is your gender?(Male=1/Female=2/Other=3)
Q2<-sample(1:3,size=500,replace=TRUE)
# Do you think marijuana legalization should be allowed?  Completely agree=1, somewhat agree=2,neutrally=3,somewhat disagree=4, completely disagree=5
Q3<-sample(1:5,size=500,replace=TRUE)
#In general, what do you think about loosened the rules for refugee?(1-5)
Q4<-sample(1:5,size=500,replace=TRUE)
# Do you think everyone should be permitted to possess guns? Yes=1,No=0
Q5<-sample(0:1,size=500,replace=TRUE)
# Do you agree with environmental safety is one of the priorities to Canada? 1-5
Q6<-sample(1:5,size=500,replace=TRUE)
# Which party are you going to vote on Election Day? 1- Liberal 2-Political 3-Quec 4-Green 5-Conservative
Q7 <- sample(1:5,size=500,replace=TRUE)

data <- data.frame(Q1,Q2,Q3,Q4,Q5,Q6,Q7)
plot(Q7)
```

